---
title: "QMM ASSIGNMET 2"
author: "SRIKANTH CHETLAPALLY"
date: "2023-09-24"
output:
  pdf_document: default
  html_document: default
---

```{r}
table=matrix(c(420,750,13000,20,900,360,900,12000,15,1200,300,450,5000,12,750),ncol=5, byrow=T)
colnames(table)=c('PROFIT','EXCESS CAP','STORAGE','UNIT','SALES')
rownames(table)=c('large','medium','small')
table
```

No of large units produced at plant1: D_l1
No of medium units produced at plant1: D_m1
No of small units produced at plant1: D_s1
No of large units produced at plant1: D_l2
No of medium units produced at plant1: D_m2
No of small units produced at plant1: D_s2
No of large units produced at plant1: D_l3
No of medium units produced at plant1: D_m3
No of small units produced at plant1: D_s3

Objective function:

$$ MAX \hspace{.3cm} Z = 420(D_l1+D_m2+D_s3)+360(D_l1+D_m2+D_s3)+300(D_l1+D_m2+D_s3)$$

Constraints

Production capacity constraints:

The production of each size at each plant should not exceed the respective plants capacity
excess capacity for each plant is 750, 900 and 400 units per day.

$$D_l1+D_m1+D_s1 \le 750$$

$$D_l2+D_m2+D_s2 \le 900$$

$$D_l3+D_m3+D_s3 \le 450$$

Storage space restrictions at present: the production of ecah size at each plant should not exceed the available in process storage space



$$20D_l1+15D_m1+12D_s1 \le 13000$$

$$20D_l2+15D_m2+12D_s2 \le 12000$$

$$20D_l3+15D_m3+12D_s3 \le 5000$$


Demand constraint:

The production of each size meet the scale forecast.

$$D_l1+D_m1+D_s1 \le 900$$

$$D_l2+D_m2+D_12 \le 1200$$

$$D_l3+D_m3+D_s3 \le 750$$

Restrictions on layoffs of employees:

$$(D_l1+D_m1+D_s1)/750 = (D_l2+D_m2+D_s2)/900 = (D_l3+D_m3+D_s3)/450$$

Non negativity constraints:

$$Dl>0,Dm > 0,Ds > 0$$
## SOLVING LP MODEL IN R

```{r}
library(lpSolve)

# Defining the sizes and plants of the weigelt corporation
sizes <- c("large","medium","small")
plants <- c("plant1","plant2","plant3")

# The profit per unit for each size of the plant

profit <- c(420, 360, 300)

# The excess production capacity for each plant
capacity <- c(750, 900, 450)

# The available in-process storage space for each plant
storage_space <- c(13000, 12000, 5000)

# The space requirement per unit for each size
space_per_unit <- c(20, 15, 12)

# The sales forecasts for each size
sales_forecast <- c(900, 1200, 750)

# Objective coefficients
obj_coef <- c(420, 360, 300, 420, 360, 300,420, 360, 300)

# Constraint matrix (left-hand side)
const_matrix <- matrix(c(
  1,1,1,0,0,0,0,0,0, 
  0,0,0,1,1,1,0,0,0,  
  0,0,0,0,0,0,1,1,1,  
  20,15,12,0,0,0,0,0,0, 
  0,0,0,20,15,12,0,0,0,  
  0,0,0,0,0,0,20,15,12, 
  1,0,0,1,0,0,1,0,0, 
  0,1,0,0,1,0,0,1,0,  
  0,0,1,0,0,1,0,0,1   
), nrow = 9, byrow = TRUE)

# Right-hand side of constraints
rhs <- c(750, 900, 450, 13000, 12000, 5000, 900, 1200, 750)

# Constraint direction (less than or equal)
const_dir <- rep("<=", 9)

# Solve the linear programming problem
lp("max", obj_coef, const_matrix, const_dir, rhs)

# Extract the solution
lp("max", obj_coef, const_matrix, const_dir, rhs)$solution
```





